\textbf{universal corpus}

### 2014-04-25 docs/computEL-final/clean.tex
added API information

Omniglot does not give codes at all, but only the language name. To resolve this issue, we automatically converted language names to codes using information from the SIL website.\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}}

@@

It is important to make sure that the data we have compiled will be available to future researchers, regardless of how the surrounding infrastructure changes. \newcite{bird2003port} describe a set of best practices for maintaining portability of digital information, outlining seven dimensions along which this can vary. Following this advice, we have ensured that all our data is available as plain text files, with utf-8 encoding, labelled with the relevant ISO 639-3 code. Metadata is stored separately. We have written an API to allow access to the data according to the guidelines of \newcite{abney2010universal}, who remain agnostic as to the specific form of data storage. If, for reasons of space or speed, an alternative format would be preferred, the data would be straightfoward to convert since it can be accessed according to these guidelines.

>>>>

Omniglot does not give codes at all, but only the language name. To resolve this issue, we automatically converted language names to codes using information from the SIL website.\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}}.

To facilitate the standardization of language code, we have written a small python API that can be used in query information about a language and its code(s). Also, a function to convert language names to their appropriate ISO 639-3 codes. If internet connection is available, the API automatically updates the ISO 639-3 file stored locally on the users harddrive before responding to the user's query. An example usage of the API is as such:

\small\begin{verbatim}
>>> from seedling import miniethnologue
>>> sil = miniethnologue.miniSIL()
>>> sil.ISO6393['eng']
{'iso6391': 'en', 
'iso6392t': 'eng',
'iso6392b': 'eng',
'name': 'English', 
'ismacro': False, 
'scope': 'Indvidual', 
'type': 'Living'}
>>> sil.name2code('German')
deu
\end{verbatim}
\normalsize

Similarly, we provide an API to access language information from the World Atlas of Language Structures (WALS). The language clustering experiment in section 5 uses this API to access the language family information.

\small\begin{verbatim}
>>> from seedling import miniwals
>>> wals = miniwals.MiniWALS()
>>> wals['eng']
{'glottocode': 'stan1293', 
'name': 'English', 
'family': 'Indo-European', 
'longitude': '0.0', 
'latitude': '52.0', 
'genus': 'Germanic', 
'macroarea': u'Eurasia'}
\end{verbatim}
\normalsize

@@

It is important to make sure that the data we have compiled will be available to future researchers, regardless of how the surrounding infrastructure changes. \newcite{bird2003port} describe a set of best practices for maintaining portability of digital information, outlining seven dimensions along which this can vary. Following this advice, we have ensured that all our data is available as plain text files, with utf-8 encoding, labelled with the relevant ISO 639-3 code. Metadata is stored separately. We have written an API to allow access to the data according to the guidelines of \newcite{abney2010universal}, who remain agnostic as to the specific form of data storage. If, for reasons of space or speed, an alternative format would be preferred, the data would be straightfoward to convert since it can be accessed according to these guidelines. SeedLing's python API can be invoked as such:

\small\begin{verbatim}
>>> from seedling import udhr
>>> for lang, sent in udhr.sents():
>>>   print lang, sent
...
eng Universal Declaration of 
Human Rights
eng Preamble
eng Whereas recognition of the 
inherent dignity and of the equal 
...
\end{verbatim}
\normalsize

Without programmatically accessing the corpus using the API, users are able to download a copy tab-delimited plaintext files and process it easily in the programming language or software of their choice.
